\texttt{timeline} Documentation

### 2016-06-17 docs/documentation/documentation.tex
documentation

@@

\subsubsection*{Time Series Plots: \texttt{api/time\_plots}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} list of time series ids
 \item[] \textbf{Description:} 
\end{itemize}

\subsubsection*{Live Time Series Plot: \texttt{api/live\_plot/\{live\_time\_series\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} last received
 \item[] \textbf{Description:} 
\end{itemize}

\subsubsection*{ACF Plot: \texttt{api/acf\_plot/\{time\_series\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} max lag, scale
 \item[] \textbf{Description:} 
\end{itemize}

\subsubsection*{Forecasting Plot: \texttt{api/forecasting\_plot/\{forecast\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} none
 \item[] \textbf{Description:} 
\end{itemize}

>>>>

In this section we want to explain how to start our project.

\begin{itemize}
\item
\textbf{go to the vagrant folder:} \texttt{cd vagrant/}
\item
\textbf{start vagrant:} \texttt{vagrant up}
\item
\textbf{start our website:} start a browser and go to \texttt{http://localhost:5000/}
\end{itemize}

Now our website should start and you can explore it.

@@

\subsubsection*{Time Series Plots: \texttt{api/time\_plots}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} list of time series ids
 \item[] \textbf{Description:} This route create the visualization primitive for a simple time plot (i.e. a time plot of all time series).
 It may return a HTTP status code 404 if no time series with the given identifier exists.
\end{itemize}

\subsubsection*{Live Time Series Plot: \texttt{api/live\_plot/\{live\_time\_series\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} last received
 \item[] \textbf{Description:} This route create the visualization primitive for a simple live time plot.
 It may return a HTTP status code 404 if no time series with the given identifier exists.
 The \texttt{last\_received} parameter must be integer that represent the last received timestamp, the start date and the new data.
\end{itemize}

\subsubsection*{ACF Plot: \texttt{api/acf\_plot/\{time\_series\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} max lag, scale
 \item[] \textbf{Description:} This route create the visualization primitive for a simple acf time plot.
 It may return a HTTP status code 404 if no time series with the given identifier exists and a HTTP status code 400 for invalid values for the optional GET parameter.
 \item[] \textbf{Additional Parameter:} All of the following parameter are optional.
 It is possible to only retrieve a slice of the time series using the \texttt{max\_lag} parameter. The parameter must be an integer.
\end{itemize}

\subsubsection*{Forecasting Plot: \texttt{api/forecasting\_plot/\{forecast\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} none
 \item[] \textbf{Description:} This route create the visualization primitive for a simple forecasting time plot.
 It may return a HTTP status code 404 if no time series with the given identifier exists.
\end{itemize}

\subsection{DATA SETS}
The task of this module is to get the values for the time series, live data and forecast data and store it in their classes.
The source code is located in the \texttt{data\_sets.py} file.

\subsubsection*{Register Data Sets:}
\begin{itemize}
 \item[] \textbf{Method:} ADD
 \item[] \textbf{Description:} In this section, we have three functions to add the data set to the \texttt{time\_series}, \texttt{live\_time\_series} or \texttt{forecast} dictionary.
\end{itemize}

\subsubsection*{Get Data Sets:}
\begin{itemize}
 \item[] \textbf{Method:} GET
 \item[] \textbf{Description:} In this section, we have different functions to get the data sets (\texttt{time\_series}, \texttt{live\_time\_series} or \texttt{forecast}). 
 There are functions to get one data set (with an id) or you can get all data sets.
\end{itemize}

\subsubsection*{class TimeSeries:}
\begin{itemize}
 \item[] \textbf{Description:} The class TimeSeries needs an id, a name, a description, the data and the legend. 
 It also has functions to get several informations like the number of samples, the start date, the end date and the period.
\end{itemize}

\subsubsection*{class LiveTimeSeries:}
\begin{itemize}
 \item[] \textbf{Description:} The class LiveTimeSeries needs a name, description and a legend.
 It also has functions to get and to update the data.
\end{itemize}

\subsubsection*{class TimeSeriesForecast:}
\begin{itemize}
 \item[] \textbf{Description:} The class TimeSeriesForecast needs a name, a description, the training data, the forecasted data, the test data and the validation split.
\end{itemize}

\subsection{FRONT END}
The task of this module is to render the different html templates.
The source code is located in the \texttt{frontend.py} file.

\subsection{VISUALIZATION}
The task of this module is to visualize the data.
The source code is located in the \texttt{visualizations.py} file.

\subsubsection*{Time Series Plot}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot, with no additional given start and end date.
\end{itemize}

\subsubsection*{Add Rolling Mean}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling mean.
\end{itemize}

\subsubsection*{Add Rolling Std}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling standard deviation.
\end{itemize}

\subsubsection*{Auto Correlation Plot}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a auto correlation time series plot with the \texttt{max\_lag} parameter.
\end{itemize}

\subsubsection*{Forecasting Eval Plot}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a forecasting time series plot.
\end{itemize}

\subsubsection*{Build Data Object}
\begin{itemize}
 \item[] \textbf{Description:} This function build the object for all other functions in this class. The object consists of a date and a value.
\end{itemize}
